Data Specialization for a Staged Lambda Calculus

### 2015-02-22 paper/splitting.tex
add some citations to intro

Since lambdas may represent multi-stage computations, 
masking splits the body of lambdas as general world \bbonem\ terms (as described in \ref{sec:split-one}), 
and packages the resulting terms as functions.

@@

Function introduction has a $\tup{}$ boundary value,
since functions are already fully reduced in our semantics.
However, since the body of a function may itself be multi-stage, splitting must continue into it.
The immediate result is a new function formed from the first-stage part of the original body.
The resumer is a new function formed out of the second-stage part of the original body.
It is the responsibility of the application site to save the precomputation of the function body
and pass it to the resumer version of the function.

>>>>

Since lambdas may represent multistage computations, 
masking splits the body of lambdas as general world \bbonem\ terms (as described in \ref{sec:split-one}), 
and packages the resulting terms as functions.

@@

Function introduction has a $\tup{}$ boundary value,
since functions are already fully reduced in our semantics.
However, since the body of a function may itself be multistage, splitting must continue into it.
The immediate result is a new function formed from the first-stage part of the original body.
The resumer is a new function formed out of the second-stage part of the original body.
It is the responsibility of the application site to save the precomputation of the function body
and pass it to the resumer version of the function.
